Capstone Movielens Report

### 2025-10-22 reports/capstone-movielens.site/05.appendix.Rmd
Logging Functions documented.
Fix for the Logging functions.

::: { #func.get_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.print_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.put_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.get_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.print_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.put_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.get_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.print_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.put_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

#--------------------------------------

@@

::: { #func.get_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.print_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

::: { #func.put_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string; can be multiline), i.e., any string containing format elements ("%1").

@@

# ------------------------------------------------------------------------------

>>>>

::: { #func.get_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.print_log1.args.msg_template .sidebar }
  - **msg_template:**Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.put_log1.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of a substring of the form `%1`.

@@

::: { #func.get_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.

@@

::: { #func.print_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.

@@

::: { #func.put_log2.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one combination of the following substrings: `%1`, `%2`.

@@

::: { #func.get_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

::: { #func.print_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

::: { #func.put_log3.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`.

@@

@@

::: { #func.get_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.

@@

::: { #func.print_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.

@@

::: { #func.put_log4.args.msg_template .sidebar }
  - **msg_template:** Message template (or format string), i.e., any (possibly multiline) string containing at least one occurrence of each of the following substrings: `%1`, `%2`, `%3`, `%4`.

@@
